An improved platform for Web service wrapping, discovery and consumption

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_introduction.tex
reference added
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@845 d8b0c59b-6544-0410-94d9-83a5658a058e

Dealing with Business-to-consumer (B2C) integration, the adoption of these standards have offered some advantages as well, however the interaction and consumption of web services requires a programming skills and understanding of many technical details about the technology, which is an obstacle for an end-user with limited knowledge on the matter. Regarding discovery, most of the publishing and discovery platforms are syntactic-base, leading to poor precision and recall, making difficult to navigate through a large variety of web services \cite{pilioura_acm2009}, and as a result not empowering the end-users to tackle easily with this task. Other solutions like Semantic Web Service promised many advantages in discovery, composition and consumption of web services, independently of the provider's platform, the location, the service implementation, or the data format. However, their adoption was not as expected [TODO: any reference?], the further requirements needed and extra work have not being seen to be worth by enterprises for the benefits they offer. In the same direction as B2C, goverments are currently opening their data to the public as linked data. So far, the efforts are being focused on data, and the users have to deal with the development of applications to use that data. It is easily to predict that sooner or later they will move to open their services for administration tasks and single-window applications. Hence, they will be benefict by the research done around these concepts and technologies.

>>>>

Dealing with Business-to-consumer (B2C) integration, the adoption of these standards have offered some advantages as well, however the interaction and consumption of web services requires a programming skills and understanding of many technical details about the technology, which is an obstacle for an end-user with limited knowledge on the matter (in the sense as defined in \cite{fuchsloch2010}). Regarding discovery, most of the publishing and discovery platforms are syntactic-base, leading to poor precision and recall, making difficult to navigate through a large variety of web services \cite{pilioura_acm2009}, and as a result not empowering the end-users to tackle easily with this task. Other solutions like Semantic Web Service promised many advantages in discovery, composition and consumption of web services, independently of the provider's platform, the location, the service implementation, or the data format. However, their adoption was not as expected [TODO: any reference?], the further requirements needed and extra work have not being seen to be worth by enterprises for the benefits they offer. In the same direction as B2C, goverments are currently opening their data to the public as linked data. So far, the efforts are being focused on data, and the users have to deal with the development of applications to use that data. It is easily to predict that sooner or later they will move to open their services for administration tasks and single-window applications. Hence, they will be benefict by the research done around these concepts and technologies.
